### 2018-06-30 FrascatiPlot/Paper/NucleiB2.tex
small fix in formulas

\begin{equation}
 \rmsradius^2 = {3 \over 2}{A - 1 \over A} r_{A}^2
\end{equation}

\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{4/3}  \rmsd$ for $A = 2$, $r_{3}= {\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{9/8} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).

>>>>

\begin{equation}
 \rmsradius^2 = {3 \over 2}{A - 1 \over A} {r_{A}^2 \over 2}
\end{equation}

\noindent for point-like constituents. In particular, we obtain $r_{d}= \sqrt{8/3}  \rmsd$ for $A = 2$, $r_{3}= \sqrt{2}{\rmsthree}$ for $A = 3$, and  $r_{4}= \sqrt{16/9} \rmsfour$ for $A=4$ (see Appendix \ref{appendix:Sato} for details).
